??

### 2018-06-12 manuscript/main.tex
Update the caption for module heat map and table for significantly associated gene expression probes

\begin{figure*}[htb!]
\centering
\includegraphics[width=0.8\textwidth]{Figures/vBsr}
\caption{\textbf{Heatmap of methylation clusters, average methylation level and gene expression probes significantly associate with average methylation level} }
\label{heatmap}
\end{figure*}

\begin{table*}[ht!]
\centering
\begin{tabular}{llr}
  \toprule
gene & description & coef \\ 
  \midrule
  Cluster 1 \\
  \midrule
ERBB2 & erb-b2 receptor tyrosine kinase 2 & 0.002 \\ 
  ZBTB38 & zinc finger and BTB domain containing 38 & -0.00068 \\ 
  HDAC2 & histone deacetylase 2 & 0.00059 \\ 
  RBPJ & recombination signal binding protein for immunoglobulin kappa J region & -0.00019 \\ 
  POU6F1 & POU class 6 homeobox 1 & 0.0023 \\ 
  TAL1 & TAL bHLH transcription factor 1, erythroid differentiation factor & 0.0002 \\ 
  CDCA7 & cell division cycle associated 7 & -0.00015 \\ 
  AURKB & aurora kinase B & 0.0004 \\ 
   \midrule
   Cluster 3 \\
   \midrule
   MED13L & mediator complex subunit 13 like & -0.00015 \\ 
  INTS6 & integrator complex subunit 6 & -0.00021 \\ 
  MGMT & O-6-methylguanine-DNA methyltransferase & 0.0006 \\ 
  SOX15 & SRY-box 15 & 0.00071 \\ 
  TRAF7 & TNF receptor associated factor 7 & 0.00028 \\ 
  ABHD14B & abhydrolase domain containing 14B & -0.00012 \\ 
  PDLIM1 & PDZ and LIM domain 1 & 1.1e-05 \\ 
  ZMYM4 & zinc finger MYM-type containing 4 & 0.00018 \\ 
   \midrule
   Cluster 5 \\
   \midrule
   TLR6 & toll like receptor 6 & 0.0007 \\ 
  SSU72 & SSU72 homolog, RNA polymerase II CTD phosphatase & 0.00013 \\ 
  BCL7A & BCL tumor suppressor 7A & 0.00021 \\ 
  SARS & seryl-tRNA synthetase & -0.0003 \\ 
  SFPQ & splicing factor proline and glutamine rich & -2.8e-05 \\ 
  \midrule
  Cluster 6 \\
  \midrule
  DEAF1 & DEAF1, transcription factor & 8.1e-05 \\ 
  ATF7IP & activating transcription factor 7 interacting protein & -5.1e-05 \\ 
  PSEN1 & presenilin 1 & -0.00022 \\ 
  CREBZF & CREB/ATF bZIP transcription factor & 0.00031 \\ 
  RBL2 & RB transcriptional corepressor like 2 & 0.00024 \\ 
  VLDLR & very low density lipoprotein receptor & -6.4e-05 \\ 
  ZC3H8 & zinc finger CCCH-type containing 8 & -0.00045 \\ 
  ZBTB24 & zinc finger and BTB domain containing 24 & 0.00015 \\ 
  \midrule
  Cluster 7 \\
  \midrule
  MAMLD1 & mastermind like domain containing 1 & -0.00059 \\ 
  AKT1 & AKT serine/threonine kinase 1 & 9e-05 \\ 
  F2RL1 & F2R like trypsin receptor 1 & -0.00015 \\ 
  GFI1 & growth factor independent 1 transcriptional repressor & 8.6e-05 \\ 
  GLO1 & glyoxalase I & -3.8e-05 \\ 
  HNMT & histamine N-methyltransferase & 0.00092 \\ 
  MED1 & mediator complex subunit 1 & -0.00018 \\ 
  PAK6 & p21 (RAC1) activated kinase 6 & 0.00033 \\ 
  ZNF286A & zinc finger protein 286A & -0.004 \\ 
  KIAA1549 & KIAA1549 & 0.00047 \\ 
  ZBED5 & zinc finger BED-type containing 5 & -0.00034 \\ 
  SCML1 & Scm polycomb group protein like 1 & -0.00043 \\ 
  CRTC3 & CREB regulated transcription coactivator 3 & -8.9e-05 \\ 
  SLC11A1 & solute carrier family 11 member 1 & 0.00019 \\ 
  TP53BP1 & tumor protein p53 binding protein 1 & 0.00032 \\ 
  CBX2 & chromobox 2 & -0.00037 \\ 
  TRIM15 & tripartite motif containing 15 & 0.0005 \\ 
   \bottomrule
\end{tabular}
\label{genes}
\caption{\textbf{Gene expression probes significantly associated with methylation cluster}}
\end{table*}

>>>>

\begin{figure*}[htb!]
\centering
\includegraphics[width=0.8\textwidth]{Figures/vBsr}
\caption{\textbf{Heat map of methylation level, average methylation level and gene expression probes significantly associate with average methylation level} For methylation cluster 1, 3, 5, 6, 7, the methylation level is shown. Methylation level within a cluster is averaged across the patients and served as response variable for vBsr model. The gene expression level of probes significantly associated with the methylation level was standardized and displayed as heat map as well. }
\label{heatmap}
\end{figure*}

\begin{table*}[ht!]
\centering
\begin{tabular}{llr}
  \toprule
gene & description & coef \\ 
  \midrule
  Cluster 1 \\
  \midrule
ERBB2 & erb-b2 receptor tyrosine kinase 2 & 0.002 \\ 
  ZBTB38 & zinc finger and BTB domain containing 38 & -0.00068 \\ 
  HDAC2 & histone deacetylase 2 & 0.00059 \\ 
  RBPJ & recombination signal binding protein for immunoglobulin kappa J region & -0.00019 \\ 
  POU6F1 & POU class 6 homeobox 1 & 0.0023 \\ 
  TAL1 & TAL bHLH transcription factor 1, erythroid differentiation factor & 0.0002 \\ 
  CDCA7 & cell division cycle associated 7 & -0.00015 \\ 
  AURKB & aurora kinase B & 0.0004 \\ 
   \midrule
   Cluster 3 \\
   \midrule
   MED13L & mediator complex subunit 13 like & -0.00015 \\ 
  INTS6 & integrator complex subunit 6 & -0.00021 \\ 
  MGMT & O-6-methylguanine-DNA methyltransferase & 0.0006 \\ 
  SOX15 & SRY-box 15 & 0.00071 \\ 
  TRAF7 & TNF receptor associated factor 7 & 0.00028 \\ 
  ABHD14B & abhydrolase domain containing 14B & -0.00012 \\ 
  PDLIM1 & PDZ and LIM domain 1 & 1.1e-05 \\ 
  ZMYM4 & zinc finger MYM-type containing 4 & 0.00018 \\ 
   \midrule
   Cluster 5 \\
   \midrule
   TLR6 & toll like receptor 6 & 0.0007 \\ 
  SSU72 & SSU72 homolog, RNA polymerase II CTD phosphatase & 0.00013 \\ 
  BCL7A & BCL tumor suppressor 7A & 0.00021 \\ 
  SARS & seryl-tRNA synthetase & -0.0003 \\ 
  SFPQ & splicing factor proline and glutamine rich & -2.8e-05 \\ 
  \midrule
  Cluster 6 \\
  \midrule
  DEAF1 & DEAF1, transcription factor & 8.1e-05 \\ 
  ATF7IP & activating transcription factor 7 interacting protein & -5.1e-05 \\ 
  PSEN1 & presenilin 1 & -0.00022 \\ 
  CREBZF & CREB/ATF bZIP transcription factor & 0.00031 \\ 
  RBL2 & RB transcriptional corepressor like 2 & 0.00024 \\ 
  VLDLR & very low density lipoprotein receptor & -6.4e-05 \\ 
  ZC3H8 & zinc finger CCCH-type containing 8 & -0.00045 \\ 
  ZBTB24 & zinc finger and BTB domain containing 24 & 0.00015 \\ 
  \midrule
  Cluster 7 \\
  \midrule
  MAMLD1 & mastermind like domain containing 1 & -0.00059 \\ 
  AKT1 & AKT serine/threonine kinase 1 & 9e-05 \\ 
  F2RL1 & F2R like trypsin receptor 1 & -0.00015 \\ 
  GFI1 & growth factor independent 1 transcriptional repressor & 8.6e-05 \\ 
  GLO1 & glyoxalase I & -3.8e-05 \\ 
  HNMT & histamine N-methyltransferase & 0.00092 \\ 
  MED1 & mediator complex subunit 1 & -0.00018 \\ 
  PAK6 & p21 (RAC1) activated kinase 6 & 0.00033 \\ 
  ZNF286A & zinc finger protein 286A & -0.004 \\ 
  KIAA1549 & KIAA1549 & 0.00047 \\ 
  ZBED5 & zinc finger BED-type containing 5 & -0.00034 \\ 
  SCML1 & Scm polycomb group protein like 1 & -0.00043 \\ 
  CRTC3 & CREB regulated transcription coactivator 3 & -8.9e-05 \\ 
  SLC11A1 & solute carrier family 11 member 1 & 0.00019 \\ 
  TP53BP1 & tumor protein p53 binding protein 1 & 0.00032 \\ 
  CBX2 & chromobox 2 & -0.00037 \\ 
  TRIM15 & tripartite motif containing 15 & 0.0005 \\ 
   \bottomrule
\end{tabular}
\label{genes}
\caption{\textbf{Gene expression probes significantly associated with methylation cluster} HGNC gene symbol, short description and vBsr coefficients of the genes significantly associated with the methylation pattern were shown in the table for cluster 1, 3, 5, 6, and 7. }
\end{table*}
